Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-26 paper.tex
Had made some changes

\documentclass{llncs}
\usepackage{graphics}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[dvips]{epsfig}
\usepackage[latin1]{inputenc}
\usepackage{url}
\usepackage{appendix}

@@

Publishing a book, in the same way as releasing any other cultural product with a
physical substrate, implies several types of risks and costs due to
the complexity, and derived expenses, of the production,
distribution and storage processes; most of these costs are associated
to the number of books actually printed. But the problem is further
complicated for completely new products, in the sense that it is an unknown
author or a new topic with no track record, sales forecasts can
only be based on the experience obtained from other similar products,
but the definition of ``similar'' itself is obscure and, sometimes,
subjective. Even if it is a known author or topic, having accurate
estimations of future sales of the new product is extremely important, so 
that production runs do not exceed predicted sales by too much. 
Indeed, several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancement in the 
production process \cite{Fildes2010,Saeed2008}.

@@

The problem is specially acute for book publishers, who, among other
content providers, release new {\em products} more frequently than
other industries, so that they face the 
problem of predicting sales quite often. The issue, in this case, is to print an
adequate number of copies but not too many, as the unsold volumes will
lead to losses and sunk inventory cost, 
whereas if the number of printed copies was not enough, a new print
run can be made, resulting in temporary losses due to lack of supply;
a real problem, to be sure, but less dire than having too many unsold
books.  
%FERGU: el you ese es muy coloquial, reescribir
% Antonio - Esto habría que matizarlo más, de hecho, decirlo va un poco en contra de nuestro artículo, ya que simplifica el problema. Yo indicaría que errores en predicciones por exceso o por defecto tienen MUCHAS pegas (ambos casos), si bien el exceso es peor, claro, pero decir que lo otro es también muy negativo y por eso hay que ajustar muy bien la predicción. ;)
% Se podría señalar, por ejemplo:
% - repetición de costes de distribución
% - mala impresión al cliente/lector, que pueden repercutir negativamente en las ventas
% - algunas más... :D
% Corregido - JJ
In this sense, errors in one or the other direction do not have the same impact.
% Antonio - esto habría que rescribirlo de acuerdo a lo anterior que comento. ;)
%FERGU: lo de one or the other direction creo que confunde
% Lo que habría que decir es hablar de cómo hemos tratado una u otra
% cosa. ¿Estamos sesgando hacia predecir menos ventas de las que
% habría? ¿O simplemente es por tener un poco de background? Igual
% deberíamos haberlas tratado de forma diferente. - JJ

Thus, it is extremely important to develop an accurate predictive method
which could forecast the future sales a new book will
achieve, in order to optimise production schedules, improve the publishing
company profits or minimise losses \cite{Zhao2001}, 
being this the main objective of this paper: optimizing sales and
improving profit margins by selling the whole print-run.

In any case, the accuracy of the predictive method we intend to design is affected
negatively by several factors, related to decisions on purchases, to freight 
traffic, or with the distribution strategy \cite{Little1998}. % This
                                % paragraph is rather useless - JJ
% I have changed the paragraph completely, but still don't know what
% this is doing here - JJ

@@

@@

As far as we know, no previous attempt can be found in the literature in which 
prediction methods have been applied to estimate the print run. 
However, similar techniques to those proposed in this paper, e.g. 
regression models \cite{Papalexopoulos1990}, 
neural networks \cite{Yoo1999} 
or fuzzy systems \cite{Mastorocostas2001}, 
have been applied to solve sales prediction problems in other industrial sectors.

@@

For this reason, usually the methods used to predict book sales have
been generally based on experts' experience.% Reference - JJ
 They analyse data about
sales and, taking into account their knowledge in industry, their
experience, and their perception about trends, could make decisions on
the companies production, i.e. how many books should be printed when a new
book is published. 
This is a complex problem, since the predictions are influenced by
external variables that must be taken into account, such as
seasonality, promotions or fashions that expert managers might
subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}. % This
                                % has something to do with the
                                % previous paragraph? Put it there!!! 
%
  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works have proposed analysing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon
et al. propose using the number of blog references as an indicator of
the success of a book, and thus, its sales. Different sales patterns
are observed by analysing data obtained. 
% Antonio - describir esos 'sales patterns'. ;)
% FERGU: y también cuales son esos 'data obtained'
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied to the problem of unpublished-books sales prediction.
%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?

@@

%--- new SOM description % -Sam

SOM is a type of unsupervised neural networks inspired by the topographical organization of the sensory cortex of human brain \cite{kohonen1998}. It maps highly dimensional data into a lower dimensional space where similar data patterns are located in more adjacent areas on the grid.

SOM is a very useful analysis tool for visualizing complex data with high number of variables in a simple geometric planes. Therefore, it could be used for different tasks like features reduction and data clustering and visualization.

Basically, SOM consists of two layers; input layer and output layer (also known as Kohen layer). Input layer is fully connected with the Kohen layer which is usually a two dimensional grid of neurons (i.e.; units). This means that every neuron is linked to every input in the input layer.

The learning process of SOM is an iterative process applied in two stages. First, the weights of the network are initialized randomly then the n-dimensional input vectors are presented to the network sequentially so the distance between the weights of the neurons and the inputs are computed using the simple Euclidean distance. In the second stage, the neuron which has the shortest distance with the presented input vector is updated along with its neighbor neurons. This neuron is called the best matching unit (BMU). The goal of the learning process is to minimize the neighborhood distance in the output clusters.

When the learning process is done a visual representation method like the Unified Distance Matrix, or U-matrix for short, is used to visualize the distances between neurons in the output space. In the U-matrix, the distance between adjacent neurons is measured and assigned different colors. Dark colors between neurons indicate large distances (boundaries) while light colors represent similar areas (clusters).

%---

%FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?
% Antonio - arreglado 
% And this is going to be useful because... - JJ

@@

***TODO***: talking about the machines used

%Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
%(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.

@@

\subsection{Results for all the editors}
\label{subsec:results_all_editors}

In the first stage of the experiments, forecasting methods have been applied to the whole dataset. All the pre-sales features have been considered, including the categorical ones, which make it harder to process the instances and build the different models. SVM for instance, must previously transform these categories into binary variables in order to deal with the data, which means the creation of a different (and new) variable per each possible value. Thus, in the case of editorial or collection this would imply the definition of hundreds of new variables.
% Antonio - Sam, verify this, please
% Sam - reviewed and fixed

@@

***TODO***: Revise and fix the following text...

@@

In the second stage of the experiments, different feature selection methods have been applied. The aim of these methods is to reduce the number of features considered in developing the forecasting models which consequently simplify the complexity of the models, improve their interpretability and decrease the training time. The simpler models generated after performing feature selection could give the decision maker a better insight on the underlying process by identifying the more influencing variables.

% Antonio - TODO: explain the aim of FS in these experiments.
% Sam : Done

@@

Case 1-A: Developing prediction models to predict Total sales for
Editorial704 (An editorial with the most number of different books sold) - 293
instances.

\begin{table}
\caption{Predicting Total sales for Editorial704}

@@

Case 1-B: Developing prediction models to predict Total sales for
Editorial-UDLU11 (An editorial with a medium number of different books sold) - 180 instances.

\begin{table}
\caption{Predicting Total sales for Editorial-UDLU11}

@@

Case 2-A: Developing prediction models to predict Total sales for
Editorial-UDL929 (The best selling editorial) - 216 instances.

\begin{table}
\caption{Predicting Total sales for Editorial-UDL929 (460752 sales) }

@@

Case 2-B: Developing prediction models to predict Total sales for
Editorial-UDLW12 (The median selling editor)- 97 instances.

\begin{table}
\caption{Predicting Total sales for Editorial-UDLW12 (2635 sales) }

@@

***TO DO***: explain we have chosen the best Feature selection method (ReliefAttributeEval???). The rest of tables have been moved to an appendix.

Case 1-A: Developing prediction models to predict Total sales for
Editorial704 with ReliefFAttributeEval feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for Editorial704 (ReliefFAttributeEval-FS) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 89.3 $\pm$0.08  & 69.70 $\pm$19.85  & 122.48 $\pm$47.28  & 38.49 $\pm$11.53  & 46.68 $\pm$16.02 & 0.028 $\pm$0.003\tabularnewline
\hline 
K-NN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.7 $\pm$0.08  & 73.13 $\pm$22.95  & 137.60 $\pm$56.14  & 39.79 $\pm$10.69  & 51.35 $\pm$17.00  & 0.13 $\pm$0.01\tabularnewline
\hline 
LR  & 87.3 $\pm$0.06  & 89.72 $\pm$18.31  & 140.65 $\pm$47.12  & 49.45 $\pm$10.50  & 53.20 $\pm$14.16  & 0.0008 $\pm$0.0005\tabularnewline
\hline 
SVM  & 87.7 $\pm$0.07  & 77.30 $\pm$22.25  & 146.46 $\pm$57.68  & 41.67 $\pm$7.99  & 53.10 $\pm$9.51  & 0.05 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\end{table}

Case 1-B: Developing prediction models to predict Total sales for
Editorial-UDLU11 with ReliefFAttributeEval feature selection

\begin{table}[!ht]
\caption{Predicting Total sales for Editorial-UDLU11 (ReliefFAttributeEval-FS)}

@@

Case 2-A: Developing prediction models to predict Total sales for
Editorial-UDL929 with ReliefFAttributeEval feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for Editorial-UDL929 (ReliefFAttributeEval-FS)}

@@

Case 2-B: Developing prediction models to predict Total sales for
Editorial-UDLW12 with ReliefFAttributeEval feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for Editorial-UDLW12 (ReliefFAttributeEval-FS)}

@@

>>>>

\documentclass{llncs}
\usepackage{graphics}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[dvips]{epsfig}
\usepackage[latin1]{inputenc}
\usepackage{url}

@@

%***TO DO***: complete this considering the new contents and results\\
% Instead of just writing this you should say what has changed and
% what should be changed. For instance, the paragraph below probably
% shouldn't - JJ 
Publishing a book, in the same way as releasing any other cultural product with a
physical substrate, implies several
types of risks and costs due to
the complexity, and derived expenses, of the production,
distribution and storage processes; most of these costs are associated
to the number of books actually printed. But the problem is further
complicated for completely new products, in the sense that it is an unknown
author or a new topic with no track record, sales forecasts can
only be based on the experience obtained from other similar products,
but the definition of ``similar'' itself is obscure and, sometimes,
subjective. Even if it is a known author or topic, having accurate
estimations of future sales of the new 
product is extremely important \cite{ChingChin2010}, so that production
runs do not exceed predicted sales by too much. 
Indeed, several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancement in the 
%FERGU: an enhancing está bien dicho? Mejor "an enhacement", no?
production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
%which should be obvious from the get go, don't know why you need 4
%papers to affirm that - JJ
%please someone address this - JJ

@@

The problem is specially acute for book publishers, who, among other
content providers, release new {\em products} more frequently than
other industries, so that they face the 
problem of predicting sales quite often. The issue, in this case, is to print an
adequate number of copies but not too many, as the unsold volumes will
lead to losses and sunk inventory cost, 
% Antonio - 'sunk inventory cost' es corecto?
% Sí, pero corecto no lo es. - JJ
whereas if the number of printed copies was not enough, a new print
run can be made, resulting in temporary losses due to lack of supply;
a real problem, to be sure, but less dire than having too many unsold
books.  
%FERGU: el you ese es muy coloquial, reescribir
% Antonio - Esto habría que matizarlo más, de hecho, decirlo va un poco en contra de nuestro artículo, ya que simplifica el problema. Yo indicaría que errores en predicciones por exceso o por defecto tienen MUCHAS pegas (ambos casos), si bien el exceso es peor, claro, pero decir que lo otro es también muy negativo y por eso hay que ajustar muy bien la predicción. ;)
% Se podría señalar, por ejemplo:
% - repetición de costes de distribución
% - mala impresión al cliente/lector, que pueden repercutir negativamente en las ventas
% - algunas más... :D
% Corregido - JJ
In this sense, errors in one or the other direction do not have the same impact.
% Antonio - esto habría que rescribirlo de acuerdo a lo anterior que comento. ;)
%FERGU: lo de one or the other direction creo que confunde
% Lo que habría que decir es hablar de cómo hemos tratado una u otra
% cosa. ¿Estamos sesgando hacia predecir menos ventas de las que
% habría? ¿O simplemente es por tener un poco de background? Igual
% deberíamos haberlas tratado de forma diferente. - JJ

Thus, it is extremely important to develop an accurate predictive method
which could forecast the future sales a new book will
achieve, in order to optimise production schedules, improve the publishing
company profits or minimise losses \cite{Zhao2001}. This is the main
objective of this paper. 
%FERGU: entonces el objetivo es desarrollar una herramienta? La
%metodología? Dejarlo más claro en todos los sitios
% Un método predictivo. Lo deja muy claro - JJ
An example is the optimisation of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. 
% Antonio - podrías extender un poco el ejemplo? Es decir, describir
% un poco más lo que se hace en ese trabajo. ;)
% An example of what? Does that go there or to the state of the art? - JJ

The accuracy of the predictive method we intend to design is affected
negatively by several factors, related to decisions on purchases, to freight 
traffic, or with the distribution strategy \cite{Little1998}. % This
                                % paragraph is rather useless - JJ
% I have changed the paragraph completely, but still don't know what
% this is doing here - JJ

@@

% We should also mention what data we actually mean, I don't think
% we've published it here. - JJ

@@

% [Pedro] no se encuentra gran cosa sobre predicción de ventas de libros
%  por eso quiero comenzar hablando de la aplicación de métodos
%  de predicción en la industria en general, que sí hay bastante bibliografía.
% Antonio - me parece bien

% Antonio - Cosas generales a mejorar en el SotA:
% - habría que comparar más veces este trabajo con lo que hacen otros, destacando nuestras diferencias. Sólo se menciona al final de la sección
% - habría que destacar claramente ls aportes de este trabajo al SotA, cómo hace que avance ;)
% - habría que incluir citas a artículos de la revista que elijamos y comentarlos aquí

% Sales forecasting is a problem which has been addressed several times
% in the literature.
% This sentence is useless
In the past, sales prediction has been performed using methods such as  regression models
\cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy 
systems \cite{Mastorocostas2001}, applied to different industrial
sectors. 
% ¿Y qué? Esta frase
% no aporta nada. La primera frase
% tiene que enmarcar el estado del
% arte - JJ
% Antonio - la he intentado mejorar.
% Muchas cosas de la intro tendrían que venir aquí, al estado del
% arte. Habría que reescribir la intro. - JJ
% ¿Qué usan esos métodos? - JJ

@@

For this reason, usually the methods used to predict book sales have
been generally based on experts' experience.% Reference - JJ
 They analyse data about
sales and, taking into account their knowledge in industry, their
experience, and their perception about trends, could make decisions on
the companies production (how many books should be printed when a new
book is published). 
%FERGU: quitad los paréntesis :)
% Fergu: quítalos tú, tío, aquí puede editar todo el mundo - JJ
This is a complex problem, since the predictions are influenced by
external variables that must be taken into account, such as
seasonality, promotions or fashions that expert managers might
subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}. % This
                                % has something to do with the
                                % previous paragraph? Put it there!!! 
%
  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works have proposed analysing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon
et al. propose using the number of blog references as an indicator of
the success of a book, and thus, its sales. Different sales patterns
are observed by analysing data obtained. 
% Antonio - describir esos 'sales patterns'. ;)
% FERGU: y también cuales son esos 'data obtained'
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied to the problem of unpublished-books sales prediction.
%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?

@@

Kohonen's SOM is a feedforward neural network \cite{Haykin98_NNC} that
uses an unsupervised training algorithm and which, through a process
called self-organisation, configures the output units into a
topological representation of the original data. It tries to imitate
the self-organisation done in the sensory cortex of the human brain,
where neighbouring neurons are activated by similar stimulus. SOM
belongs to a general class of neural network methods, which are
non-linear regression techniques that can be trained to learn or find
relationships between inputs and outputs or to organise data so as to
disclose so far unknown patterns or structures. It is usually used as
a clustering/classification tool or used to find unknown relationships
between a set of variables that describe a problem. The main property
of the SOM is that it makes a nonlinear projection from a
high-dimensional data space (one dimension per variable) on a regular,
low-dimensional (usually 2D) grid of neurons, called units. 
SOM is further processed using Ultsch method \cite{UmatUlts}, the
Unified distance matrix (U-matrix), which uses SOM's codevectors
(vectors of variables of the problem) as data source and generates a
matrix where each component is a distance measure between two adjacent
neurons. It allows us to visualise any multi-variated dataset in a
two-dimensional display, so we can detect topological relations among
neurons and infer about the input data structure. High values in the
U-matrix represent a frontier region between clusters, and low values
represent a high degree of similarities among neurons on that region,
clusters .

SOMs (and U-Matrix) are usually applied to visualise natural
structures in the data and their relations, as well as the natural
groupings that could be among them. In addition, SOM makes easy the
estimation of the variables that have more influence on these
groupings. Other statistical and soft computing tools can also be used
for this purpose, but since Kohonen's SOMs offers a visual way of
doing it, it is much more intuitive, and takes advantage of the
capabilities of the human brain as a pattern recogniser. 
%FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?
% Antonio - arreglado 
% And this is going to be useful because... - JJ
% This is copied from the HIV paper. Please rephrase and adapt to the
% particular venue - JJ

@@

%***TODO***: talking about the machines used
% Please don't use real text for TODOs- JJ
%Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
%(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.

@@

\subsection{Results for all editors}
\label{subsec:results_all_editors}

In the first experiment, forecasting methods have been applied to the
whole dataset. All the pre-sales features have been considered, also
including the categorical ones, which make harder to process the
instances and build the different models. SVM for instance, must
previously transform these categories into numbers in order to deal
with the data, which means the creation of a different (and new)
variable per possible value. Thus, in the case of editorial or
collection this would imply the definition of hundreds of new
variables. 
% Antonio - Sam, verify this, please
% Sam is Hossam? - JJ

@@

%***TODO***: Revise and fix the following text...

@@

In this second experiment, different feature selection processes have been applied.

***TODO***: The aim of these techniques is to reduce the number of features to consider...
% Antonio - TODO: explain the aim of FS in these experiments.

@@

Case 1-A: Developing prediction models to predict Total sales for
Editor704 (An editor with the most number of different books sold) - 293
instances.

\begin{table}
\caption{Predicting Total sales for Editor704}

@@

Case 1-B: Developing prediction models to predict Total sales for
Editor-UDLU11 (An editor with a medium number of different books sold) - 180
instances.

\begin{table}
\caption{Predicting Total sales for Editor-UDLU11}

@@

Case 2-A: Developing prediction models to predict Total sales for
Editor-UDL929 (The best selling editor) - 216 instances.

\begin{table}
\caption{Predicting Total sales for Editor-UDL929 (460752 sales) }

@@

Case 2-B: Developing prediction models to predict Total sales for
Editor-UDLW12 (The median selling editor)- 97 instances.

\begin{table}
\caption{Predicting Total sales for Editor-UDLW12 (2635 sales) }

@@

***TO DO***: choose the best Feature selection method and apply just this one (ReliefAttributeEval???). There are too many tables I think.
We could add an appendix or so with the rest of results if you want.

Case 1-A: Developing prediction models to predict Total sales for
Editor704 with ReliefFAttributeEval feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for Editor704 (ReliefFAttributeEval-FS) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 89.3 $\pm$0.08  & 69.70 $\pm$19.85  & 122.48 $\pm$47.28  & 38.49 $\pm$11.53  & 46.68 $\pm$16.02 & 0.028 $\pm$0.003\tabularnewline
\hline 
K-NN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.7 $\pm$0.08  & 73.13 $\pm$22.95  & 137.60 $\pm$56.14  & 39.79 $\pm$10.69  & 51.35 $\pm$17.00  & 0.13 $\pm$0.01\tabularnewline
\hline 
LR  & 87.3 $\pm$0.06  & 89.72 $\pm$18.31  & 140.65 $\pm$47.12  & 49.45 $\pm$10.50  & 53.20 $\pm$14.16  & 0.0008 $\pm$0.0005\tabularnewline
\hline 
SVM  & 87.7 $\pm$0.07  & 77.30 $\pm$22.25  & 146.46 $\pm$57.68  & 41.67 $\pm$7.99  & 53.10 $\pm$9.51  & 0.05 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\end{table}

Case 1-A: Developing prediction models to predict Total sales for
Editor704 with CfsSubsetEval feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for Editor704 (CfsSubsetEval-FS)}

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 80.1 $\pm$0.09 & 104.87 $\pm$21.38 & 174.57 $\pm$47.33 & 58.11 $\pm$14.73 & 67.58 $\pm$22.61 & 0.018 $\pm$0.003\tabularnewline
\hline 
K-NN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & 170.83 $\pm$46.34 & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 77.6 $\pm$0.13 & 101.93 $\pm$23.66 & 180.56 $\pm$51.20 & 56.10 $\pm$13.62 & 69.86 $\pm$23.27 & 0.0738 $\pm$0.003\tabularnewline
\hline 
LR & 80.1 $\pm$0.10 & 106.62 $\pm$21.52 & 173.18 $\pm$46.58 & 59.11 $\pm$14.96 & 67.53 $\pm$24.53 & 0.0004 $\pm$0.0005\tabularnewline
\hline 
SVM & 81.8 $\pm$0.08 & 94.29 $\pm$25.52 & 180.54 $\pm$62.67 & 50.79 $\pm$8.48 & 65.62 $\pm$6.25 & 0.040 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\end{table}

Case 1-A: Developing prediction models to predict Total sales for
Editor704 with SOM feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for Editor704 (SOM-FS)}

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 89.2 $\pm$0.07 & 71.536 $\pm$18.95 & 123.06 $\pm$42.13 & 39.43 $\pm$10.58 & 47.20 $\pm$15.16 & 0.031 $\pm$0.007\tabularnewline
\hline 
K-NN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 87.7 $\pm$0.08 & 73.98 $\pm$20.91 & 134.11 $\pm$51.70 & 40.48 $\pm$10.51 & 50.41 $\pm$16.38 & 0.10 $\pm$0.0076\tabularnewline
\hline 
LR & 87.5 $\pm$0.06 & 88.70 $\pm$16.34 & 135.03 $\pm$35.18 & 49.08 $\pm$10.47 & 51.97 $\pm$13.65 & 0.0006 $\pm$0.0005\tabularnewline
\hline 
SVM & 87.8 $\pm$0.06 & 81.09 $\pm$22.48 & 154.82 $\pm$59.93 & 43.65 $\pm$7.36 & 55.72 $\pm$7.15 & 0.031 $\pm$0.003\tabularnewline
\hline 
\end{tabular}
\end{table}

Case 1-B: Developing prediction models to predict Total sales for
Editor-UDLU11 with ReliefFAttributeEval feature selection

\begin{table}[!ht]
\caption{Predicting Total sales for Editor-UDLU11 (ReliefFAttributeEval-FS)}

@@

Case 1-B: Developing prediction models to predict Total sales for
Editor-UDLU11 with CfsSubsetEval feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for Editor-UDLU11 (CfsSubsetEval-FS)}

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 64.0 $\pm$0.23 & 777.94 $\pm$342.04 & 1305.28 $\pm$1075.29 & 78.37 $\pm$30.4 & 99.86 $\pm$85.43 & 0.013 $\pm$0.001\tabularnewline
\hline 
K-NN & 64.8 $\pm$0.18 & 702.70 $\pm$181.41 & 1008.39 $\pm$305.87 & 71.41 $\pm$13.95 & 78.47 $\pm$22.70 & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 65.3 $\pm$0.19 & 685.56 $\pm$195.28 & 1021.37 $\pm$352.88 & 69.74 $\pm$16.96 & 79.37 $\pm$26.98 & 0.0466 $\pm$0.0023\tabularnewline
\hline 
LR & 67.0 $\pm$0.23\ & 857.22 $\pm$308.69 & 1352.26 $\pm$945.31 & 86.10 $\pm$24.25 & 102.89 $\pm$74.43 & 0.0003 $\pm$0.0005\tabularnewline
\hline 
SVM & 64.8 $\pm$0.23 & 879.91 $\pm$280.33 & 1402.82 $\pm$593.44 & 87.74 $\pm$15.27 & 105.40 $\pm$37.73 & 0.017 $\pm$0.001\tabularnewline
\hline 
\end{tabular}
\end{table}

Case 1-B: Developing prediction models to predict Total sales for
Editor-UDLU11 with SOM feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for Editor-UDLU11 (SOM-FS)}

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 79.0 $\pm$0.14 & 573.25 $\pm$167.88 & 827.55 $\pm$388.16 & 58.42 $\pm$14.14 & 63.98 $\pm$25.63 & 0.0153 $\pm$0.0015\tabularnewline
\hline 
K-NN & 83.6 $\pm$0.10 & 492.18 $\pm$126.86 & 727.33 $\pm$209.88 & 50.12 $\pm$10.69 & 56.14 $\pm$12.89 & 0 $\pm$0.0002\tabularnewline
\hline 
RF & 85.6 $\pm$0.08 & 446.25 $\pm$119.79 & 673.46 $\pm$189.06 & 45.38 $\pm$9.78 & 52.24 $\pm$13.09 & 0.0594 $\pm$0.0049\tabularnewline
\hline 
LR & 71.0 $\pm$0.19 & 723.74 $\pm$247.96 & 1108.74 $\pm$736.17 & 74.14 $\pm$24.91 & 85.96 $\pm$59.99 & 0.0004 $\pm$0.0005\tabularnewline
\hline 
SVM & 71.6 $\pm$0.15 & 640.14 $\pm$206.46 & 1017.02 $\pm$376.13 & 63.96 $\pm$11.87 & 76.10 $\pm$16.80 & 0.019 $\pm$0.001\tabularnewline
\hline 
\end{tabular}
\end{table}

Case 2-A: Developing prediction models to predict Total sales for
Editor-UDL929 with ReliefFAttributeEval feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for Editor-UDL929 (ReliefFAttributeEval-FS)}

@@

Case 2-A: Developing prediction models to predict Total sales for
Editor-UDL929 with CfsSubsetEval feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for Editor-UDL929 (CfsSubsetEval-FS)}

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 88.0 $\pm$0.13 & 738.28 $\pm$188.53 & 1141.79 $\pm$472.025 & 45.45 $\pm$13.62 & 47.58 $\pm$24.84 & 0.017 $\pm$0.002\tabularnewline
\hline 
K-NN & 85.3 $\pm$0.15& 825.19 $\pm$235.34 & 1280.33 $\pm$523.06 & 50.23 $\pm$14.07 & 51.42 $\pm$21.24 & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 86.4 $\pm$0.14 & 790.09 $\pm$225.86 & 1245.23 $\pm$584.23 & 48.22 $\pm$13.79 & 50.01 $\pm$21.97 & 0.063 $\pm$0.0039\tabularnewline
\hline 
LR & 86.6 $\pm$0.12 & 936.56 $\pm$204.46 & 1329.24 $\pm$480.79 & 58.04 $\pm$16.92 & 55.41 $\pm$25.62 & 0.0004 $\pm$0.0005\tabularnewline
\hline 
SVM & 86.8 $\pm$0.12 & 940.39 $\pm$344.16 & 1648.50 $\pm$1026.04 & 54.50 $\pm$7.12 & 56.17 $\pm$7.8 & 0.020 $\pm$0.002\tabularnewline
\hline 
\end{tabular}
\end{table}

Case 2-A: Developing prediction models to predict Total sales for
Editor-UDL929 with SOM feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for Editor-UDL929 (SOM-FS)}

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 89.7 $\pm$0.10 & 685.67 $\pm$185.99 & 1116.42 $\pm$478.06 & 42.09 $\pm$12.8 & 46.31 $\pm$24.61 & 0.02 $\pm$0.004\tabularnewline
\hline 
K-NN & 89.0 $\pm$0.10 & 746.45 $\pm$250.76 & 1203.41 $\pm$564.84 & 44.36 $\pm$9.73 & 46.25 $\pm$14.41 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 89.5 $\pm$0.09 & 708.24 $\pm$264.52 & 1270.26 $\pm$708.82 & 42.14 $\pm$12.45 & 49.07 $\pm$26.59 & 0.080 $\pm$0.0058\tabularnewline
\hline 
LR & 86.6 $\pm$0.13 & 894.08 $\pm$206.60 & 1282.83 $\pm$451.87 & 55.29 $\pm$15.92 & 53.74 $\pm$24.70 & 0.0005 $\pm$0.0005\tabularnewline
\hline 
SVM & 87.1 $\pm$0.10 & 908.56 $\pm$348.20 & 1608.77 $\pm$972.55 & 52.63 $\pm$8.75 & 55.95 $\pm$12.49 & 0.022 $\pm$0.002\tabularnewline
\hline 
\end{tabular}
\end{table}

Case 2-B: Developing prediction models to predict Total sales for
Editor-UDLW12 with ReliefFAttributeEval feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for Editor-UDLW12 (ReliefFAttributeEval-FS)}

@@

Case 2-B: Developing prediction models to predict Total sales for
Editor-UDLW12 with CfsSubsetEval feature selection.

\begin{table}[!ht]
\caption{Predicting Total sales for Editor-UDLW12 (CfsSubsetEval-FS)}
